Model exploration

### 2015-04-22 documentation/model_exploration.Rmd
model_exploration.Rmd; return simulation data and plot attractor

```{r, echo = FALSE, fig.cap="", fig.height = 2}

@@

parms$f = 1
bifurcation(parms, pairapprox = TRUE, meanfield = FALSE, "b", c(0,1)) -> out_1

parms$f = 0.5
bifurcation(parms, pairapprox = TRUE, meanfield = FALSE, "b", c(0,1), add =TRUE) -> out_2

parms$f = 0
bifurcation(parms, pairapprox = TRUE, meanfield = FALSE, "b", c(0,1), add =TRUE) -> out_3

@@

parms$f = 1
bifurcation(parms, pairapprox = TRUE, meanfield = FALSE, "L", c(0,12))-> out_4

parms$f = 0.5
bifurcation(parms, pairapprox = TRUE, meanfield = FALSE, "L", c(0,12), add =TRUE)-> out_5

parms$f = 0
bifurcation(parms, pairapprox = TRUE, meanfield = FALSE, "L", c(0,12), add =TRUE)-> out_6

>>>>

```{r, echo = FALSE, fig.cap="", fig.height = 2, warning=FALSE}

@@

parms$f = 1
bifurcation(parms, pairapprox = TRUE, meanfield = FALSE, "b", c(0,1), returnoutput = TRUE) -> out_1

parms$f = 0.5
bifurcation(parms, pairapprox = TRUE, meanfield = FALSE, "b", c(0,1), add =TRUE, returnoutput = TRUE) -> out_2

parms$f = 0
bifurcation(parms, pairapprox = TRUE, meanfield = FALSE, "b", c(0,1), add =TRUE, returnoutput = TRUE) -> out_3

@@

parms$f = 1
bifurcation(parms, pairapprox = TRUE, meanfield = FALSE, "L", c(0,12), returnoutput = TRUE)-> out_4

parms$f = 0.5
bifurcation(parms, pairapprox = TRUE, meanfield = FALSE, "L", c(0,12), add =TRUE, returnoutput = TRUE)-> out_5

parms$f = 0
bifurcation(parms, pairapprox = TRUE, meanfield = FALSE, "L", c(0,12), add =TRUE, returnoutput = TRUE)-> out_6

  plot(out_1$pairapprox$rho_11, out_1$pairapprox$q_11, pch = 20,  cex = 0.5, ylim = c(0,1), xlim = c(0,1))
 points(out_2$pairapprox$rho_11, out_2$pairapprox$q_11, pch = 20,  cex = 0.5)
 points(out_3$pairapprox$rho_11, out_3$pairapprox$q_11, pch = 20,  cex = 0.5)
 points(out_4$pairapprox$rho_11, out_4$pairapprox$q_11, pch = 20,  cex = 0.5)
 points(out_5$pairapprox$rho_11, out_5$pairapprox$q_11, pch = 20,  cex = 0.5)
 points(out_6$pairapprox$rho_11, out_6$pairapprox$q_11, pch = 20,  cex = 0.5)
abline(a = 0, b = 1, lty = 3, col = "#D0D0D0")
points(0,0, pch=20, col = "white", cex = 2)
 points(0,0, pch=20, cex = 0.5)
